---
title: "Old Faithful exploratory analysis"
author: "Louise Carr"
date: "11/11/2020"
output: html_document
---
# Introduction
The Old Faithful data set contains the waiting time between eruptions and the duration of the eruption for the Old Faithful geyser in Yellowstone National Park, Wyoming, USA.

First load the data

``` {r} 
df<-faithful 
```

The data description is given in the table below

| Variable  |   Description                                    | 
|---------:|  :-----------------------------------------------|
| Eruption |   The duration of the eruption, minutes           | 
| Waiting  |   waiting time to next eruption, minutes          | 


A summary of the distributions of each variable are as follows: 
``` {r} 
summary(df)
```

The marginal distributions of the variable shown below:
``` {r} 
hist(df$eruptions)
```
```{r} 
hist(df$waiting)
```

# Updated analysis

Both the duration of eruptions and waiting time show a bimodal distribution.
```{r} 
plot(df$eruptions,df$waiting)
```